Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-06-05 awipev-CO2.Rmd
fixed knitting issue

#{.tabset .tabset-fade .tabset-pills}

##Infos

###**Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

###**AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

@@

###**Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

@@

##Total alkalinity

@@

###**Filtration of AT data: outliers removing**

@@

###**Correction of AT data**

@@

####**Calibration**

@@

####**CRM measurements**

@@

####**Discrete samples ("references")**

@@

#####**Third period**

@@

#####**Second period**

@@

###**Discrete total alkalinity (reference) vs salinity relationship**

@@

###**seaFET calibration constante E0**

@@

###**seaFET pHT calibrated**
pH is measured continuously by an autonomous seaFET pH sensor. Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16). To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.

@@

###**durafet calibration**

@@

###**seaFET / durafet pHs**

@@

###**calculated / durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

###**calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
psf_calc_norm_text

@@

##Maintenance
<div style="text-align: justify">

###**REMOS**
- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.

###**FerryBox**
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

###**TA analyser**
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

###**pH seaFET**
- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed. Continuous mode with external power supply was set and internal pack of baterries was removed. Old seaFET will be brought back to France with Samir.
- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.

@@

###***p*CO~2~**
- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.

@@

##Script + data
<div style="text-align: justify">  
Here is reported all important modifications made on *ny-alesund_cc.*.
All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:

@@

###**pH seaFET**
- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling"). See seaFET part.
- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).

###**durafet**
Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off. This reference point was not takken in consideration for calibration. The window of the previous and next calibration periods was extended.

###***p*CO~2~**
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

###**SNAPO**
- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements. Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater. We will ad a lack of DIC for this week. TA will be measured in Villefranche.
- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).

###**Files - server**
- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04). This adding was put in comments now. In seaFET data reading, S/N have been changed from 1005 to 0007.
- **2018-03-21**: Files issues. FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK. Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder. They were in SBE38 folder...Weird. Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not. Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed. File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.

@@

**Data processing**

>>>>

# {.tabset .tabset-fade .tabset-pills}

## Infos

### **Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

### **AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

@@

### **Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

@@

## Total alkalinity

@@

### **Filtration of AT data: outliers removing**

@@

### **Correction of AT data**

@@

#### **Calibration**

@@

#### **CRM measurements**

@@

#### **Discrete samples ("references")**

@@

##### **Third period**

@@

##### **Second period**

@@

### **Discrete total alkalinity (reference) vs salinity relationship**

@@

### **seaFET calibration constante E0**

@@

### **seaFET pHT calibrated**
pH is measured continuously by an autonomous seaFET pH sensor. Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16). To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.

@@

### **Durafet calibration**

@@

### **seaFET / durafet pHs**

@@

### **Calculated vs Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
psf_calc_norm_text

@@

## Maintenance
<div style="text-align: justify">

### **REMOS**
- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.

### **FerryBox**
- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

### **TA analyser**
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

### **pH seaFET**
- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed. Continuous mode with external power supply was set and internal pack of baterries was removed. Old seaFET will be brought back to France with Samir.
- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.

@@

### ***p*CO~2~**
- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.

@@

## Script + data
<div style="text-align: justify">  
Here is reported all important modifications made on *ny-alesund_cc.*.
All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:

@@

### **pH seaFET**
- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling"). See seaFET part.
- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).

### **Durafet**
Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off. This reference point was not takken in consideration for calibration. The window of the previous and next calibration periods was extended.

### ***p*CO~2~**
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

### **SNAPO**
- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements. Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater. We will ad a lack of DIC for this week. TA will be measured in Villefranche.
- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).

### **Files - server**
- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04). This adding was put in comments now. In seaFET data reading, S/N have been changed from 1005 to 0007.
- **2018-03-21**: Files issues. FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK. Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder. They were in SBE38 folder...Weird. Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not. Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed. File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.

@@

** Data processing**
